---
title: "Network_HW2"
author: "Chenrui Xu"
date: "2021/2/13"
output: html_document
---

```{r}
library(statnet)
library(UserNetR)
library(RColorBrewer)
set.seed(123)
```

Part 1 setting matrix
```{r}
netmat=rbind(c(1,2), #1
             c(1,3), #2
             c(1,4), #3
             c(1,5), #4
             c(1,6), #5
             c(1,7), #6
             c(1,8), #7
             c(1,9), #8
             c(1,10),#9
             c(1,11),#10
             c(1,12),#11
             c(1,13),#12
             c(1,14),#13
             c(1,15),#14
             c(1,16),#15
             c(1,17),#16
             #c(2,1), #17 #1
             c(2,3), #18
             c(2,4), #19
             c(2,8), #20
             c(2,13),#21
             c(2,14),#22
             c(2,15),#23
             c(2,16),#24
             #c(3,1), #25 #2
             #c(3,2), #26 #18
             c(3,4), #27
             c(3,8), #28
             c(3,9), #29
             c(3,13),#30
             #c(4,1), #31 #3
             #c(4,2), #32 #19
             #c(4,3), #33 #27
             c(4,8), #34
             c(4,12),#35
             c(4,13),#36
             #c(5,1), #37 #4
             c(5,7), #38
             c(5,10),#39
             #c(6,1), #40 #5
             c(6,7), #41
             c(6,10)#42
             #c(7,1), #43 #6
             #c(7,5), #44 #38
             #c(7,6), #45 #41
             #c(8,1), #46 #7
             #c(8,2), #47 #20
             #c(8,3), #48 #28
             #c(8,4), #49 #34
             #c(9,1), #50 #8
             #c(9,3), #51 #29
             #c(10,1),#52 #9
             #c(10,5),#53 #39
             #c(10,6),#54 #42
             #c(11,1),#55 #10
             #c(12,1),#56 #11
             #c(12,4),#57 #35
             #c(13,1),#58 #12
             #c(13,2),#59 #21
             #c(13,3),#60 #30
             #c(13,4),#61 #36
             #c(14,1),#62 #13
             #c(14,2),#63 #22
             #c(15,1),#64 #14
             #c(15,2),#65 #23
             #c(16,1),#66 #15
             #c(16,2),#67 #24
             #c(17,1) #68 #16
)
```

```{r}
net <- network(netmat,matrix.type="edgelist",directed = FALSE)

network.vertex.names(net)<-c("a1","a2","a3","a4","a5","a6","a7","a8","a9","a11","a12","a13","a14","a18","a20","a22","a32")
```
Turn matrix into edgelist network data and give them nodes names.


Part2
```{r}
set.vertex.attribute(net,"role",c('lightblue','lightblue','lightblue','lightblue','lightblue','lightblue','lightblue','lightblue',"pink",'lightblue','lightblue','lightblue','lightblue','lightblue','lightblue','lightblue','pink'))
```
Give nodes the role attributes and set nodes colors.

```{r}
#set.vertex.attribute(net,"shape",c(4,4,4,4,4,4,4,4,10000,4,4,4,4,4,4,4,10000))
set.vertex.attribute(net,"shape",c(1,1,1,1,1,1,1,1,2,1,1,1,1,1,1,1,2))
```
Give nodes the shape attributes as 4 is the square and circle we can view it as infinite of edges shape square.

```{r}
set.edge.attribute(net,"ecolor",c('royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4'))
```
in terms of edges, we can set color to be royalblue and gold

The setting of the width, we put it into gplot() and according to the plot shown in the Powerpoint, we can set the numbers.
```{r}
set.seed(123)
rolelab=net%v%"role"
shape=net%v%"shape"
my_pal <- c('lightblue','pink')
ecolor=net%e%"ecolor"
op <- par(mar=c(0,0,0,0))
gplot(net,gmode="graph",
      mode="fruchtermanreingold",
      vertex.cex=2.5,
      main="FruchtermanReingold",
      vertex.col =rolelab,
      displaylabels=T,
      label.pos=5,
      vertex.sides =c(4,10000)[shape],vertex.rot=45,#let square shape rotate 45
      edge.lwd=c(10,12,8,8,8,8,6,6,6,4,8,2,8,4,4,4,16,8,10,12,2,4,4,8,10,12,8,8,8,8,4,8,12,8),
               # 1  2  3 4 5 6 7 8 9 0 1 2 3 4 5 6 7  8 9  0  1 2 3 4 5  6  7 8 9 0 1 2 3  4
               # 0                 1                       2                      3
      edge.col = ecolor
      )
par(op)
```

Part 3
```{r}
deg=degree(net,gmode = "graph")
deg
```

```{r}
rescale=function(nchar,low,high){
  min_d=min(nchar)
  max_d=max(nchar)
  rscl=((high-low)*(nchar-min_d))/(max_d-min_d)+low
  rscl
}
```

```{r}
n_edge=network.edgecount(net)
edge_cat=sample(1:4,n_edge,replace=T)
```

```{r}
set.edge.attribute(net,"ecolor",c('royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','gold1','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4','royalblue4'))
ecolor=net%e%"ecolor"
```


```{r}
my_pal=c("skyblue","pink")
rolecat=as.factor(get.vertex.attribute(net,"role"))
```


```{r}
set.seed(123)
op=par(mar=c(0,0,0,0),mfrow=c(1,2))
plot(net,
     mode="fruchtermanreingold",
     usearrows=F,
     vertex.cex=rescale(deg,5,8),
     main="Adjusted node sizes with rescale function",
     displaylabels=T,
     edge.lty=c(2,3,4,5)[edge_cat],#"solid"
     #edge.lty=b,#c('solid','dashed','dotted','dotdashed'),#[edge_cat],
     vertex.col=my_pal[rolecat],
     label.pos=5,
     vertex.sides =c(4,10000)[shape],vertex.rot=45,#let square shape rotate 45
     edge.lwd=c(10,12,8,8,8,8,6,6,6,4,8,2,8,4,4,4,16,8,10,12,2,4,4,8,10,12,8,8,8,8,4,8,12,8),
     edge.col = ecolor
     )
legend("bottomleft",
       legend=c("A","B"),
       col=my_pal,pch=15,
       pt.cex=1.5,
       bty="n",
       title="role"
       )
par(op)
```

```{r}
op=par(mar=c(0,0,0,0),mfrow=c(1,2))
gplot(net,
     mode="fruchtermanreingold",
     usearrows=F,
     vertex.cex=rescale(deg,2,6),
     main="Adjusted node sizes with rescale function",
     displaylabels=T,
     edge.lty=c(2,3,4,5)[edge_cat],
     vertex.col=my_pal[rolecat],
     label.pos=5,
     vertex.sides =c(4,10000)[shape],vertex.rot=45,#let square shape rotate 45
     edge.lwd=c(10,12,8,8,8,8,6,6,6,4,8,2,8,4,4,4,16,8,10,12,2,4,4,8,10,12,8,8,8,8,4,8,12,8),
     edge.col = "gray50"
     )
legend("bottomleft",
       legend=c("A","B"),
       col=my_pal,pch=19,
       pt.cex=1.5,
       bty="n",
       title="role"
       )
par(op)
```


```{r}

```
