---
title: "Network_HW4"
author: "Chenrui Xu"
date: "2021/2/28"
output: html_document
---

```{r}
library(UserNetR)
library(statnet)
library(igraph)
```

```{r}
data(hwd)
h1=hwd
```

```{r}
V(h1)$name[1:10]
```

```{r}
V(h1)$name[155:165]
```

```{r}
V(h1)$type[1:10]
```


```{r}
V(h1)$type[155:165]
```
So we can get that the first 160 index are the movies and from 161, the rest of them are actors.


Here is the summary of the data.
```{r}
h1
```
There are 1365 nodes and 1600 edges (160 movies and 1205 actors). There are a few attributes in the data: name, type(to show 2-mode),year, rating, etc.

```{r}
#if type is group, we use square to represent node, if it is actor, use circle
V(h1)$shape <- ifelse(
   V(h1)$type==TRUE,
   "square","circle")

#same idea to use corresponding color
V(h1)$color <- ifelse(
   V(h1)$type==TRUE,
   "red","lightblue")
```

```{r}
#create a subgraph that filter three movies to analysis
h2 <- subgraph.edges(h1, 
E(h1)[inc(V(h1)[name %in%
c("The Wolf of Wall Street", 
  "Gangs of New York",
  "The Departed")])])
plot(h2, layout = layout_with_kk)
```

```{r}
#to show number of movies each actor has, 955 actors engaged in one movie
#only one actor has 8 moives and it turned out to be HarryPorter
table(degree(h1,v=V(h1)[type==FALSE]))

#average number of movies each actor has
mean(degree(h1,v=V(h1)[type==FALSE]))

V(h1)$deg <- degree(h1)
V(h1)[type==FALSE & deg > 4]$name
#to show the actor that has more than 4 moives
```


```{r}
busy_actor <- data.frame(cbind(Actor = V(h1)[type==FALSE& deg > 4]$name,Movies = V(h1)[type==FALSE& deg > 4]$deg))
busy_actor[order(busy_actor$Movies,decreasing=TRUE),]
# to show the busy actors and their corresponding number of movies
```

```{r}
for (i in 161:1365) {
  V(h1)[i]$totrating <- sum(V(h1)[nei(i)]$IMDBrating)
}

for (i in 161:1365) {V(h1)[i]$avgrating <- mean(V(h1)[nei(i)]$IMDBrating)
}
```

```{r}
V(h1)[161:171]$totrating
```

```{r}
V(h1)[161:171]$avgrating
```

```{r}
pop_actor <- data.frame(cbind(Actor = V(h1)[type==FALSE & totrating > 40]$name,Popularity =V(h1)[type==FALSE &totrating > 40]$totrating))

pop_actor[order(pop_actor$Popularity,decreasing=TRUE),]
```

```{r}
num <- V(h1)[type==FALSE]$deg
avgpop <- V(h1)[type==FALSE]$avgrating
totpop <- V(h1)[type==FALSE]$totrating

op <- par(mfrow=c(1,2))
plot(num,totpop)
plot(num,avgpop)
par(op)
```

```{r}
summary(lm(avgpop~num))
```
There is no significance to show the more movies the actor has the more population the actor is.

The average rating of numbers of movies are around 7.5
```{r}
boxplot(avgpop~num)
```

Projection
```{r}
h1.pr <- bipartite.projection(h1)
h1.act <- h1.pr$proj1
h1.mov <- h1.pr$proj2
h1.act
h1.mov
```

```{r}
op <- par(mar = rep(0, 4))
plot(h1.mov,vertex.color="red",
   vertex.shape="circle",
   vertex.size=(V(h1.mov)$IMDBrating)-3,
   vertex.label=NA)
par(op)
```

```{r}
graph.density(h1.mov)
no.clusters(h1.mov)
clusters(h1.mov)$csize
table(E(h1.mov)$weight)
```

```{r}
h2.mov <- induced.subgraph(h1.mov,vids=clusters(h1.mov)$membership==1)

plot(h2.mov,vertex.color="red",
edge.width=sqrt(E(h1.mov)$weight),
vertex.shape="circle",
vertex.size=(V(h2.mov)$IMDBrating)-3,
vertex.label=NA)

```

```{r}
table(graph.coreness(h2.mov))
h3.mov <- induced.subgraph(h2.mov,vids=graph.coreness(h2.mov)>4)
h3.mov

plot(h3.mov,vertex.color="red",
vertex.shape="circle",
edge.width=sqrt(E(h1.mov)$weight),
vertex.label.cex=0.7,
vertex.label.color="darkgreen",
vertex.label.dist=0.3,
vertex.size=
   (V(h3.mov)$IMDBrating)-3)


```

Part II  Bradley Cooper
```{r}
    h4 <- subgraph.edges(h1, 
    E(h1)[inc(V(h1)[name %in%
    c("Bradley Cooper")])])
    plot(h4, layout = layout_with_kk)
```

```{r}
V(h4)[type==TRUE]$name
```

```{r}
h5 <- subgraph.edges(h1, 
E(h1)[inc(V(h1)[name %in%c(V(h4)[type==TRUE]$name)
])])
plot(h5, layout = layout_with_kk)
```

Part III
```{r}
summary(h3.mov)
V(h3.mov)
```

```{r}
SW3 <- induced.subgraph(h1.mov,vids=c(V(h1.mov)[nei("Star Wars: Episode III - Revenge of the Sith")],V(h1.mov)[name%in%"Star Wars: Episode III - Revenge of the Sith"]))
```

```{r}
plot(SW3, layout = layout_with_kk,,vertex.color="red",
vertex.shape="circle",
edge.width=sqrt(E(h1.mov)$weight),
vertex.label.cex=0.7,
vertex.label.color="darkgreen",
vertex.label.dist=0.3,
vertex.size=(V(h1.mov)$IMDBrating)-3)
```

```{r}


```